Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-07-27 writing/ehp_results.tex
Work on draft throughout

@@

We first calculated summary statistics for the exposure assessments
(Table~\ref{tab:exposuresummaries}). There was wide variation in the average
number of county exposures per year under the five different tropical cyclone
metrics considered. For the tornado metric, there were approximately~50 county
exposures identified per year, on average, within our study.  For flood and
wind metrics, there were substantially more county exposures identified ($>$200
per year on average), and even more when assessing exposure using the distance
and rain metrics ($>$400 per year on average).

We also measured the average number of county exposures per tropical cyclone,
within those tropical cyclones in which at least one county was exposed to the
hazard (Table~\ref{tab:exposuresummaries}). The typical number of county
exposures per tropical cyclone was lowest when assessing exposure using the
tornado metric (median:~7 county exposures per tropical cyclone), higher under
the flood and wind metrics (median:~26 and~34, respectively), and even higher
for the metrics of rain (median:~68) and distance (median:~84).  For every
metric except the tornado-based metric, we identified at least one tropical
cyclone with over~300 counties exposed.  However, the largest-extent tropical
cyclone varied by metric (e.g., Beryl in~1994 exposed the most counties based
on distance, Frances in~2004 based on rain, and Ike in~2008 based on wind).

\subsection*{Agreement in county-specific exposure classification to specific
tropical cyclones}

The counties that were identified as exposed to a tropical cyclone differed
substantially depending on which metric was used in exposure assessment.  This
was true both when comparing exposure assessment based on distance versus the
four hazard-specific metrics considered (wind, rain, floods, and tornadoes)
and also when comparing exposure assessments among the four hazard-specific
metrics.

Figure~\ref{fig:ivanexposure} gives an example of how sensitive county-level
tropical cyclone exposure assessment is to the choice of metric, using as an
example Hurricane Ivan in 2004, which was record-breaking for its
duration as a major hurricane~\citep{franklin2006atlantic}. When county-level
exposure was determined based on distance, the counties assessed as exposed
followed the tropical cyclone's track, including counties well inland. For the
wind metric, only counties near two of the tropical cyclone's landfalls were
assessed as exposed. For rain- and flood-based metrics, however, exposure
extended to the left of the track, including counties as far north as New York
and Connecticut, while for the tornado metric, exposed counties tended to be to
the right of the track and included several counties in central North Carolina,
South Carolina, and Georgia that were not identified as exposed to Ivan based
on any other metric.  Figure~S3 provides similar maps for four other example
tropical cyclones (selected because they exposed many \ac{US}  counties based on
at least one metric), and Figure~S4 provides four examples of tropical cyclones
in which the disagreement in exposure assessment between rain- and wind-based
metrics was particularly notable.

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (the period for which all five metrics were available)
for which~250 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}). In this figure, each row provides results for a
specific tropical cyclone, and each box in that row shows a measure of
agreement between a specific pair of metrics in terms of the counties assessed
as exposed to that tropical cyclone, with darker colors representing greater
agreement in county-level exposure assessments.

For most tropical cyclone, distance-based county-level exposure assessment was
at best in moderate agreement with exposure assessments based on the four
hazard-based metrics. For almost all tropical cyclones, Jaccard index values
between distance and any of the four hazard-based metrics were~0.6 or lower
(i.e., out of the counties assessed as exposed to the tropical cyclone by at
least one of the two metrics considered,~60\si{\percent} or fewer of the
counties had the same exposure assessment under the two metrics). For many
tropical cyclones, the Jaccard index values were~0.2 or lower, suggesting very
poor agreement in exposure assessment between the metrics.  Among the four
hazard-based metrics, the tornado-based metric showed universally poor
agreement with other metrics in county-level classification across all tropical
cyclones considered.  For other pairs of metrics, there were also generally
large differences in which counties were determined to be exposed to the
tropical cyclone, with the Jaccard index values below~0.4 for most metric pairs
in most tropical cyclones.

There were, however, a few exceptions\,---\,tropical cyclones in which similar
counties were determined to be exposed to the tropical cyclone for two or more
of the metrics considered.  For Floyd in~1999 (Figure~S3) and Irene in~2011,
for example, county-level classification agreed moderately to well (Jaccard
index of approximately~0.5\,--\,0.8) for all pairs of exposure metrics except
those including the tornado-based metric. These tropical cyclones both made
their first \ac{US}  landfall in North Carolina at minor hurricane windspeeds
(Category~2 and~1, respectively) and then skimmed the eastern coast of the
\ac{US} north through New England, bringing large rainfall to much of the
eastern coast from North Carolina north and causing extensive inland flooding
in North Carolina (Floyd) and New England (Irene)~\citep{avila2013atlantic,
lawrence2000atlantic}. For another set of tropical cyclones (e.g., Lee in~2011
[Figure~S3], Ernesto in~2006, and Bertha in~1996), there was moderate to good
agreement for all pairwise combinations of distance, rain, and wind, but poor
agreement for all other combinations of metrics. Most of these tropical
cyclones either followed the eastern coastline north of North Carolina (Bertha
in~1996, Charley in~2004, Gaston in~2004, Barry in~2007, and Hanna in~2008), in
a pattern similar to Hurricanes Floyd in~1999 and Irene in~2011, or made
landfall in or near the Florida panhandle and cut across to exit into the
Atlantic around North Carolina (Josephine in~1996, Earl in~1998, Alberto
in~2006). However, these two sets of tropical cyclones represented the minority
of all tropical cyclones considered; for most tropical cyclones, there was low
overlap in the counties determined to be exposed to the tropical cyclones
between most pairings of metrics.

\subsection*{Geographic patterns in tropical cyclone exposures}

When the average number of exposures per decade in each county were calculated,
strong geographical patterns were clear across tropical cyclone exposure
assessments based on these different metrics
(Figure~\ref{fig:averageexposure}). Wind-based exposure had a strong coastal
pattern, with almost all exposures in counties within about~200
\si{\kilo\metre} (124~mi) of the coastline. While exposures by rain- and
distance-based metrics were also more common in coastal areas compared to
inland areas, inland exposures were much more common based on these two metrics
compared to the wind-based metric. Rain and, to some extent, flood exposures
were characterized by a pattern defined by the Appalachian Mountains, with much
lower exposures west of the mountain range than to the east. Almost all
tornado-based exposures were in coastal states, with most in Florida, Alabama,
South Carolina, and North Carolina and almost none north of Maryland.
Flood-based exposures were highest in North Carolina and along the South
Carolina coast, as well as further north in New Jersey, southeastern
Pennsylvania, and southeastern New York. Notably, some areas of the \ac{US}
that experienced regular exposures to tropical cyclone-related excessive
rainfall and floods were not identified as areas of regular risk based on the
more commonly used tropical cyclone exposure assessment metrics of wind or
distance (Figure~\ref{fig:averageexposure}).

We conducted a case study to investigate how these differences in exposure
assessment across the five metrics considered could strongly influence
health-related studies based on physical exposure to tropical cyclones. For
this example, we compared estimates of which \ac{US} counties have the largest
expected physical exposure to tropical cyclones among a susceptible
subpopulation, Medicare beneficiaries who are reliant on electricity for
medical equipment (Figure~S6)~\citep{empower}.  We found
that a few counties (Miami-Dade County, FL; Harris County, TX) were ranked in
the top three counties of physical exposure among electricity-dependent
Medicare beneficiaries for almost all exposure metrics
(Figure~\ref{fig:topelecdependexposure}). However, there were key differences
when using different exposure metrics. For example, Florida counties dominated
the lists of top exposed counties based on wind- and tornado-based metrics,
while over half of the counties for the flood-based metric were in Mid-Atlantic
states (PA, NY).

\subsection*{Software}

To assist with future tropical cyclone impact studies, we created and published
open source software that includes the hazard-specific, county-level tropical
cyclone data in this paper, as well as tools to explore and map that 
data~\citep{hurricaneexposure, hurricaneexposuredata}. This software includes continuous
data for the distance-, rain-, and wind-based metrics, allowing users to also explore
different thresholds of these metrics when assessing exposure.

We investigated how well these data correspond with data from other available
sources (Figures~S7\,--\,11). Within the nine sample counties, storm-related
rainfall from the reanalysis precipitation dataset was well-correlated with
station-based rainfall measurements, although the reanalysis data did tend to
somewhat underestimate rainfall totals in storms with extremely high rainfall
(Figure~\ref{fig:raincomparison}). A distance constraint (county population
mean center within~500 \si{\kilo\metre} of the storm's closest approach) was
necessary for assessing storm exposure based on this metric to ensure that
rains unrelated and far from the storm track were not misattributed to storm
exposures. We found that this distance constraint was typically adequately
large to capture storm-related rain, although in rare examples of exceptionally
large storms (e.g., Hurricane Ike in 2008) or storms for which tracking was
stopped at extratropical transition (e.g., Tropical Storm Lee in 2011), some
storm-related rains were missed because of this distance constraint
(Figure~\ref{fig:rainexamples}).  The modeled wind speeds generally agreed well
with the \ac{HURDAT2} wind radii (Figure~\ref{fig:windcomparison}), with
disagreement mostly limited to large storms that were characterized by high
winds well inland (e.g., Hurricanes Ike in 2008 and Sandy in 2012;
Figure~\ref{fig:windexamples}).  Stream gage data generally indicated higher
discharge in these counties on dates identified as flood events, particularly
in counties with more reporting stream gages (e.g., Harris County, TX, with~10
reporting stream gages; Figure~\ref{fig:floodcomparison}), although these two
flooding data sources were not completely consistent.

While generally in agreement with data from other
sources, there are a few limitations. The wind data are based on modeled,
rather than observed, values, and while the modeled wind data generally agree
well with post-analysis maximum wind radii from the revised Atlantic hurricane
database \ac{HURDAT2}~\citep{landsea2013} (Figure~S7), for a few tropical cyclones
it did not (e.g., Figure~S10). The rainfall data are from re-analysis data,
which are generally well-correlated with observed ground-based station data but
sometimes oversmooth extreme measurements (Figure~S8).

>>>>

\subsection*{Exposure assessment data, data validation, and software}

\paragraph{Open-source dataset}

We created and published open source data with multi-year, county-level
tropical cyclone exposure data for eastern \ac{US}
counties~\parencite{hurricaneexposuredata}. These data include continuous
county-level measurements for the closest distance of each storm, cumulative
rainfall, and maximum sustained surface wind speed. These continuous metrics
can be used for classifying counties as exposed or unexposed, using thresholds
selected by the user, or can be used as continuous metrics. The dataset also
include binary data on flood and tornado events associated with each storm in
each county. With these data, we published software tools to explore and map
the data and to integrate it with human health
datasets~\parencite{hurricaneexposure}.

We explored potential limitations in these data by comparing them with data
from other available sources.

\paragraph{Rainfall data validation}

For estimates of storm-associated rainfall, we compared estimates from NLDAS-2
re-analysis precipitation data (included as the rainfall estimates in the
open-source data) with ground-based observations in nine sample counties
(Figure~\ref{fig:raincomparison}). Within these counties, storm-related
rainfall measurements were well-correlated between the two data sources, with
rank correlations (bottom right of each graph in
Figure~\ref{fig:raincomparison}) between 0.87 and 0.98. There was some evidence
that the reanalysis data may tend to underestimate rainfall totals in storms
with extremely high rainfall, based a few heavy-rainfall storms in Harris
County, TX, Mobile County, AL, Charleston County, SC, and Wake County, NC
(Figure~\ref{fig:raincomparison}). However, even in these cases, it was rare
for a storm to be classified differently (based on the precipitation threshold
of 75~\si{\milli\metre} we used for exposure classification for later analysis)
based on the source of precipitation data---horizontal and vertical lines in
each small plot in Figure~\ref{fig:raincomparison} show the threshold of
75~\si{\milli\metre}, so storms in the lower left and upper right quadrants
would be classified the same (``exposed'' or ``unexposed'') regardless of the
precipitation data source, while storms in the upper left and lower right
quadrants would be classified differently.

\paragraph{Wind speed data validation}

For maximum sustained surface wind speed estimates, we found that the modeled
estimates, which we included as the primary wind exposure metric in the open
source data and used for further analysis in this study, generally agreed well
with estimates based on the wind radii reported in \ac{HURDAT2}. For most
storms, $\ge$95\% of counties were assigned the same category of wind speed
($<$34~\si{\knot}; 34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot};
$\ge$64~\si{\knot}) by both data sources (Figure~\ref{fig:windcomparison}).
Disagreement was limited to large storms that were characterized by high winds
well inland, like Hurricanes Sandy in 2012 and Ike in 2008. For these two
storms, the modeled wind speed values somewhat overestimated the extent of the
storm's most severe winds at landfall but then underestimated the extent of
34\,--\,49.9 \si{\knot} storm winds further inland (Figure~S6). For researchers
who would like to conduct sensitivity analysis between these two sets of wind
data, we have included estimates from the \ac{HURDAT2} wind radii as a
secondary measure of wind speeds in the open-source dataset
\parencite{hurricaneexposuredata}.

\paragraph{Flood data validation}

For flood data, we compared the flood status measurements, based on event
listings in the NOAA Storm Events database, to streamflow measurements at
\ac{US} Geological Survey gages within nine sample counties
(Figure~\ref{fig:floodcomparison}). Each small plot in
Figure~\ref{fig:floodcomparison} shows results for one of the sample counties.
Each point represents a single tropical storm, and the point's position along
the x-axis shows the highest daily total streamflow (cubic feet per second),
summed across all identified streamgages in the county, for a five-day window
centered on the day of the storm's closest approach to the county. The y-axis
separates storms for which a flood event was reported in NOAA's Storm Events
database for the county with a start date within the five-day window of the
storm's closest approach to the county. The color of each point gives the
percent of streamflow gages in the county with a daily streamflow that exceeded
a threshold of flooding on any day during the five-day window.  Stream gage
data generally indicated higher discharge in these counties on dates identified
as flood events, particularly in counties with more reporting stream gages
(e.g., Harris County, TX, with~10 reporting stream gages;
Figure~\ref{fig:floodcomparison}). There were some cases, however, where the
two flooding data sources were not completely consistent. 
For example, there
were one or two tropical cyclones in several of the counties (Mobile County,
AL, Escambia County, FL, and Montgomery County, PA) which were classified as
flood events based on NOAA storm event listings but for which the total
discharge across county streamflow gages was below the 25\textsuperscript{th}
percentile of measurements during storms without a flood event listing. 
For tropical cyclones that did not have an associated flood listing in 
the NOAA Storm Events database, most had lower total streamflow discharge
across county gages compareed to storms with flood event listings, and in all
cases but one none of the gages were over the flooding threshold. The exception
was \ldots in Fulton County, GA. [More on which storm and why---I think there
was already a flood event that had started earlier, so it missed the cutoff for
the startdate being within the range.]

[For discussion?] Based on these results, the two data sources were generally
in agreement, but the analysis highlights the difficulty of assessing
storm-related flooding at a multi-county, multi-year scale, as flooding can be
very localized within a county or can \ldots .

@@

We used the storm exposure metrics to classify counties as exposed or unexposed
to specific tropical cyclones, and we explored patterns in these exposure
classifications over years with available data
(Table~\ref{tab:exposuresummaries}). Across the five exposure metrics, there
was wide variation in the average number of county exposures per year. For the
tornado metric, there were approximately~50 county exposures per
year, on average, within our study.  For flood and wind metrics, there were
substantially more county exposures ($>$200 / yr on average), and
even more when assessing exposure using the distance and rain metrics ($>$400 /
yr on average).

We also measured the average number of county exposures per storm under each
exposure metric (limiting this analysis to the tropical cyclones that exposed
at least one county to that hazard; Table~\ref{tab:exposuresummaries}).
Tropical cyclones typically exposed only a few counties, if any, to tornadoes
(median counties exposed per storm:~7), more counties under the flood and wind
metrics (median:~26 and~34, respectively), and even more counties for the
metrics of rain (median:~68) and distance (median:~84).  For every metric
except the tornado-based metric, we identified at least one tropical cyclone
with over~300 counties exposed.  However, the largest-extent tropical cyclone
varied by metric (e.g., Beryl in~1994 exposed the most counties based on
distance, Frances in~2004 based on rain, and Ike in~2008 based on wind).

When we calculated and mapped the average number of exposures per decade in
each county for each exposure metric (Figure~\ref{fig:averageexposure}), strong
geographical patterns were clear. Wind-based exposure had a strong coastal
pattern, with almost all exposures in counties within about~200
\si{\kilo\metre} (124~mi) of the coastline. While exposures by rain- and
distance-based metrics were also more common in coastal areas compared to
inland areas, they also created inland exposures that were not identified by
the wind-based metric. Rain and, to some extent, flood exposures were
characterized by a pattern defined by the Appalachian Mountains, with much
lower exposures west of the mountain range than to the east. Almost all
tornado-based exposures were in coastal states, with most in Florida, Alabama,
South Carolina, and North Carolina and almost none north of Maryland.
Flood-based exposures were highest in North Carolina and along the South
Carolina coast, as well as further north in New Jersey, southeastern
Pennsylvania, and southeastern New York. Notably, some areas of the \ac{US}
that experienced regular exposures to tropical cyclone-related excessive
rainfall and floods were not identified as areas of regular risk based on the
more commonly used tropical cyclone exposure assessment metrics of wind or
distance (Figure~\ref{fig:averageexposure}). Patterns were similar when
analysis was restricted to years with all exposure data available
(1996\,--\,2011; Figure~S5).

\subsection*{Agreement in county-specific exposure classification between exposure metrics}

Next, we measured the agreement between exposure classifications for each pair
of metrics. We found that these exposure classifications typically did not
strongly agree between pairs of metrics, indicating that the set of counties
identified as exposed based on one metric can have limited overlap with the
set of counties identified as exposed to the storm by another metric.

Figure~\ref{fig:ivanexposure} shows Hurricane Ivan in 2004 as an example. For
the distance-based metric, the counties assessed as exposed followed the
tropical cyclone's track, including counties well inland. For the wind metric,
only counties near two of the tropical cyclone's landfalls were assessed as
exposed. For rain- and flood-based metrics, however, exposure extended to the
left of the track, including counties as far north as New York and Connecticut,
while for the tornado metric, exposed counties tended to be to the right of the
track and included several counties in central North Carolina, South Carolina,
and Georgia that were not identified as exposed to Ivan based on any other
metric. Figure~S3 provides similar maps for four other example tropical
cyclones (selected because they exposed many \ac{US}  counties based on at
least one metric), and Figure~S4 provides four examples of tropical cyclones in
which the disagreement in exposure assessment between rain- and wind-based
metrics was particularly notable.

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (the period for which all five metrics were available)
for which~250 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}). In this figure, each row provides results for a
specific tropical cyclone, and each box in that row shows the measured Jaccard
coefficient between two of the exposure metrics for that storm.  For most
tropical cyclones, distance-based county-level exposure assessment was at best
in moderate agreement with exposure assessments based on the four hazard-based
metrics. For almost all tropical cyclones, Jaccard index values between
distance and any of the four hazard-based metrics were~$\le0.6$ (i.e., out of
the counties assessed as exposed to the tropical cyclone by at least one of the
two metrics considered,~60\si{\percent} or fewer of the counties had the same
exposure assessment under the two metrics). For many tropical cyclones, the
Jaccard index values were~$\le0.2$, suggesting very poor agreement in exposure
assessment between the metrics.  Among the four hazard-based metrics, the
tornado-based metric showed universally poor agreement with other metrics in
county-level classification across all tropical cyclones considered.  For other
pairs of metrics, there were also generally large differences in which counties
were determined to be exposed, with the Jaccard index values~$<0.4$ for most
metric pairs in most tropical cyclones.

\begin{comment}
Storms are displayed within
clusters that have similar patterns in county-level exposure agreement for
metric pairs, based on hierarchical clustering using the complete link
method~\parencite{murtagh2012algorithms} (i.e., storms in the same cluster tend
to have similar patterns for the pairwise strength of agreement among metrics);
columns are also ordered based on hierarchical clustering. 
Maps are
available showing the counties identified as exposed under each of five metrics
for the widest-extent storm in each cluster: Hurricane Ivan in~2004
(Figure~\ref{fig:ivanexposure}) and Hurricanes Floyd in~1999, Lee in~2011, Cindy
in~2005, and Katrina in~2005 (Figure~S3).
\end{comment}

There were, however, a few exceptions\,---\,tropical cyclones in which similar
counties were determined to be exposed to the tropical cyclone for two or more
of the metrics considered.  For Floyd in~1999 (Figure~S3) and Irene in~2011,
for example, county-level classification agreed moderately to well (Jaccard
index of~$\sim 0.5\mbox{\,--\,}0.8$) for all pairs of exposure metrics except
those including the tornado-based metric. For another set of tropical cyclones
(e.g., Lee in~2011 [Figure~S3], Ernesto in~2006, and Bertha in~1996), there was
moderate to good agreement for all pairwise combinations of distance, rain, and
wind, but poor agreement for all other combinations of metrics. However, these
two sets of tropical cyclones represented the minority of all tropical cyclones
considered; for most tropical cyclones, there was low overlap in the counties
determined to be exposed to the tropical cyclones between most pairings of
metrics.

\subsection*{Case study}

Finally, we conducted a case study to investigate how these differences in
exposure assessment across the exposure metrics could affect estimates of
expected physical exposure among a vulnerable subpopulation,
electricity-dependent Medicare beneficiaries.
Figure~\ref{fig:topelecdependexposure} shows the study counties with the
highest expected physical exposures in this subpopulation based on each
exposure metric. A few counties (Miami-Dade County, FL; Harris County, TX) were
ranked in the top three counties of physical exposure for almost all exposure
metrics (Figure~\ref{fig:topelecdependexposure}). However, there were key
differences when using different exposure metrics. For example, Florida
counties made up most of the counties counties with highest expected physical
exposure based on wind- and tornado-based metrics, while over half of the
counties with highest expected physical exposures for the flood-based metric
were in Mid-Atlantic states (PA, NY).

### 2019-07-27 writing/ehp_tables.tex
Work on draft throughout

\begin{table}%[tbhp] 
\centering 
\caption{Exposure metrics considered to assess county-level exposure to 
tropical cyclones}
\begin{tabular}{p{1.5cm}p{2.5cm}p{10cm}} 
\toprule
Metric & Available & Criteria for exposure \\ \midrule 
Distance & 1988--2015 & County population mean center within 100 \si{\kilo\metre} of storm track \\ 
Rain & 1988--2011 & County cumulative rainfall of 75 millimeters or more over the period from two days before to one day after the storm's closest approach and county population mean center within 500 \si{\kilo\metre} of the storm track \\ 
Wind & 1988--2015 & Modeled maximum sustained wind speed at the county's population mean center 15 meters per second or higher during the storm\\ 
Flood & 1996--2015 & Flood event listed in the \ac{NOAA} Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 \si{\kilo\metre} of the storm track \\
Tornado & 1996--2015 & Tornado event listed in the \ac{NOAA} Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 \si{\kilo\metre} of the storm track\\
\bottomrule 
\end{tabular} 
\label{tab:exposuremetrics} 
\end{table}

>>>>

\begin{table}%[tbhp] 
\centering 
\caption{Exposure metrics considered to assess county-level exposure to 
tropical cyclones}
\begin{tabular}{p{1.5cm}p{2.5cm}p{10cm}} 
\toprule
Metric & Available & Criteria for exposure \\ \midrule 
Distance & 1988\,--\,2015 & Storm track came within 100~\si{\kilo\metre} of county population mean center\\ 
Rain & 1988\,--\,2011 & County cumulative rainfall of $\ge$75~\si{\milli\metre} over the period from two days before to 
one day after the storm's closest approach and the storm track came within 500~\si{\kilo\metre} of the county population mean center\\ 
Wind & 1988\,--\,2015 & Modeled storm-associated maximum sustained winds of $\ge$15~\si{\metre\per\second}
at the county's population mean center\\ 
Flood & 1996\,--\,2015 & Flood event listed in the \ac{NOAA} Storm Events database for the county with a start date within two days of the storm's closest approach and the storm track came within 500~\si{\kilo\metre} of the county population mean center \\
Tornado & 1996\,--\,2015 & Tornado event listed in the \ac{NOAA} Storm Events database for the county with a start date within two days of the storm's closest approach and the storm track came within 500~\si{\kilo\metre} of the county population mean center\\
\bottomrule 
\end{tabular} 
\label{tab:exposuremetrics} 
\end{table}
